---
title: "Project MOSAIC"
description: |
  An NSF-funded project supporting Mathematics, Statistics, and Computation
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(mosaic)
library(ggformula)
library(mosaicCalc)
theme_set(theme_bw())
```

## Project MOSAIC

**Project MOSAIC** is a community of educators working to develop a new way to introduce mathematics, statistics, computation and modeling to students in colleges and universities.

From 2009 to 2016, Project MOSAIC was supported by a grant from the US National Science Foundation (NSF DUE-0920350).  The core resources developed during that time continue to be maintained and expanded.

Among those resources are:

- The `{mosaic}` package for R which supports teaching stats using a expressive, compact, and consistent formula syntax. This minimizes start up costs for students and enables students to calculate descriptive statistics, create statistical graphics, and construct statistical graphics. `{mosaic}` is one of three main syntaxes for teaching and doing statistics using R. (For a comparison, see Prof. Amelia McNamara's [video presentation](https://www.youtube.com/watch?v=aq5SrjXZDy4).) 

    Hundreds of instructors have found `{mosaic}` helpful in teaching 
    introductory statistics.  Example:
    
```{r echo=TRUE, indent = "    "}
Stats <- df_stats(births ~ wday, data = Births2015, 
                  center = mean, conf = ci.mean(0.95))
Stats
```


- The `{ggformula}` package, which enables ggplot2 graphics to be generated
using the formula syntax. Example:

```{r echo=TRUE, indent = "    "}
gf_jitter(births ~ wday, data = Births2015, alpha = 0.5) %>%
  gf_errorbar(conf_lower + conf_upper ~ wday, data = Stats, 
              color = ~ wday, inherit=FALSE)
```

- The **LittleApps** developed with the [MAA StatPREP](www.statprep.org) project. These are data- and graphics-centric tools for teaching introductory statistics without coding. See [the LittleApps site](http://www.statprep.org/LittleAppSite/) for more information.

- A complete [***MOSAIC Calculus***](http://ProjectMOSAIC.github.io/MOSAIC-Calculus) course including an online, freely accessible textbook, exercises, and symbolic software in R, all following the Project MOSAIC philosophy of building courses around *modeling*, using *data*, and integrating *computing* directly into the subject matter. 

- Online, freely accessible texts for teaching statistics that are coordinated with the `{mosaic}` R package.
    - [*Statistical Modeling: A Fresh Approach*](https://dtkaplan.github.io/SM2-bookdown/) by Daniel Kaplan
    - [End-of-chapter exercises for *Statistical Modeling*](go/SM2-Problems.pdf). Answers are available to instructors upon request.
    - [*Statistical Modeling: Computational Technique*](go/SM2-technique/index.html) by Daniel Kaplan and Frank Shaw. This booklet introduces the R language commands for the methods introduced in *A Fresh Approach*.
    

